### 2025-03-15 paper/sections/other/constraints.qmd
vamooooos

$$
\frac{\partial}{\partial\theta_{y^+,d}} \left(\text{div}(\mathbf{x},\mathbf{x^\prime},\mathbf{y};\theta)\right) = \frac{\partial}{\partial\theta_{y^+,d}} \left( \left(-\mathbf{M}_\theta(\mathbf{x})[y^+]\right) - \left(-\mathbf{M}_\theta(\mathbf{x}^\prime)[y^+]\right) \right) = x_{d}^\prime - x_{d}
$$ {#eq-grad}

@@

Since $(\mu_{y^-,d_{\text{immtbl}}} < \mu_{y^+,d_{\text{immtbl}}})$ we are more likely to have $(x_{d_{\text{immtbl}}}^\prime - x_{d_{\text{immtbl}}}) < 0$ than vice versa at initialization. Similarly, we are more likely to have $(x_{d_{\text{mtbl}}}^\prime - x_{d_{\text{mtbl}}}) > 0$ since $(\mu_{y^-,d_{\text{mtbl}}} > \mu_{y^+,d_{\text{mtbl}}})$.

>>>>

$$
\frac{\partial}{\partial\theta_{y^+,d}} \left(\text{div}(\mathbf{x}^+,\mathbf{x^\prime},\mathbf{y};\theta)\right) = \frac{\partial}{\partial\theta_{y^+,d}} \left( \left(-\mathbf{M}_\theta(\mathbf{x}^+)[y^+]\right) - \left(-\mathbf{M}_\theta(\mathbf{x}^\prime)[y^+]\right) \right) = x_{d}^\prime - x^+_{d}
$$ {#eq-grad}

@@

Since $(\mu_{y^-,d_{\text{immtbl}}} < \mu_{y^+,d_{\text{immtbl}}})$ we are more likely to have $(x_{d_{\text{immtbl}}}^\prime - x^+_{d_{\text{immtbl}}}) < 0$ than vice versa at initialization. Similarly, we are more likely to have $(x_{d_{\text{mtbl}}}^\prime - x^+_{d_{\text{mtbl}}}) > 0$ since $(\mu_{y^-,d_{\text{mtbl}}} > \mu_{y^+,d_{\text{mtbl}}})$.

### 2025-03-15 paper/sections/other/grids.qmd
vamooooos

using DotEnv
DotEnv.load!()
```

@@

### Accuracy

@@

imgfname = "plausibility_distance_from_target.png"
fig_caption = "Average outcomes for the plausibility measure across hyperparameters."
full_paths = joinpath.(data_dirs, joinpath(suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption) 
_str = join(include_img_commands, "\n\n")
println(_str)
```

@@

imgfname = "distance.png"
fig_caption = "Average outcomes for the cost measure across hyperparameters."
full_paths = joinpath.(data_dirs, joinpath(suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption)
_str = join(include_img_commands, "\n\n")
println(_str)
```

@@

### Accuracy

@@

### Accuracy

>>>>

using DotEnv
DotEnv.load!()

img_width = 80
```

@@

Predictive performance measures for this grid search are shown in @tbl-acc-gen.

@@

imgfname = "plausibility_distance_from_target.png"
fig_caption = "Average outcomes for the plausibility measure across hyperparameters. This shows the % change from the baseline model for the distance-based implausibility metric (@eq-impl-dist). Boxplots indicate the variation across evaluation runs and test settings (varying parameters for *ECCo*)."
full_paths = joinpath.(data_dirs, joinpath(suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption, width=img_width) 
_str = join(include_img_commands, "\n\n")
println(_str)
```

@@

imgfname = "distance.png"
fig_caption = "Average outcomes for the cost measure across hyperparameters. This shows the % change from the baseline model for the distance-based cost metric [@wachter2017counterfactual]. Boxplots indicate the variation across evaluation runs and test settings (varying parameters for *ECCo*)."
full_paths = joinpath.(data_dirs, joinpath(suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption, width=img_width)
_str = join(include_img_commands, "\n\n")
println(_str)
```

@@

Predictive performance measures for this grid search are shown in @tbl-acc-pen.

@@

Predictive performance measures for this grid search are shown in @tbl-acc-train.

### 2025-03-15 paper/sections/other/main_results.qmd
vamooooos

df = final_params(res_dir)
get_table_inputs(df, nothing; backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; table_type=:tabular)
```

@@

Final hyperparameters used for the main results for the different datasets.

>>>>

df = final_params(res_dir)
float_cols = ["decision_threshold", "lambda_energy_reg"]
get_table_inputs(df, nothing; backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; table_type=:tabular, formatters=PrettyTables.ft_round(2, findall([x in float_cols for x in names(df)])))
```

@@

Final hyperparameters used for the main results preseneted in @sec-experiments. Any hyperparameter not shown here is set to its default value (@nte-train-default).

### 2025-03-15 paper/sections/other/training.qmd
vamooooos

@@

>>>>

```{julia}
projectdir = splitpath(pwd()) |>
    ss -> joinpath(ss[1:findall([s == "CounterfactualTraining.jl" for s in ss])[1]]...) 
cd(projectdir)

using CTExperiments
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.StatsBase
using Logging

using DotEnv
DotEnv.load!()
```

@@

### Default Hyperparameters

@nte-train-default presents the default hyperparameters used during training.

::: {#nte-train-default .callout-note}

## Training Phase

```{julia}
#| output: asis

dict = Logging.with_logger(Logging.NullLogger()) do 
    CTExperiments.to_dict(Experiment()) 
end
println(CTExperiments.dict_to_quarto_markdown(dict, filter_empty=false))
```

:::

## Evaluation Details {#sec-app-eval}

@nte-eval-default presents the default hyperparameters used during evaluation.

::: {#nte-eval-default .callout-note}

## Evaluation Phase

```{julia}
#| output: asis

dict = Logging.with_logger(Logging.NullLogger()) do  
    CTExperiments.to_dict(EvaluationConfig(ExperimentGrid()))
end
println(CTExperiments.dict_to_quarto_markdown(dict, filter_empty=false))
```

:::

### 2025-03-15 paper/sections/other/tuning.qmd
vamooooos

imgfname = "plausibility_distance_from_target.png"
fig_caption = "Average outcomes for the plausibility measure across key hyperparameters."
full_paths = joinpath.(data_dirs, joinpath(ce_suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption) 
_str = join(include_img_commands, "\n\n")
println(_str)
```

>>>>

imgfname = "plausibility_distance_from_target.png"
fig_caption = "Average outcomes for the plausibility measure across key hyperparameters. This shows the % change from the baseline model for the distance-based implausibility metric (@eq-impl-dist). Boxplots indicate the variation across evaluation runs and test settings (varying parameters for *ECCo*)."
full_paths = joinpath.(data_dirs, joinpath(ce_suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption) 
_str = join(include_img_commands, "\n\n")
println(_str)
```
